---
title: "Relationship between dopamine D2 receptor availability and cognitive performance"
author: "Maria Lee"
date: "1/31/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Change to actual location 
knitr::opts_knit$set(root.dir = "~/ownCloud/FLB457_psychosis/DerivedData/Cognition")

library(dplyr) #For data wrangling
library(readxl) 
library(ppcor) #For partial correlation
library(ggplot2) #To make plots
library(cowplot) #To arrange several ggplots next to one another
library(gridGraphics) #To arrange several ggplots next to one another

#Load BPND files
load("/Users/marialee/ownCloud/FLB457_psychosis/DerivedData/BPND/BPND_values_FreeSurfer.Rdata")
bpnd <- TidyAll_FreeSurfer
#View(bpnd) #To look at the data.frame and available variables. 
bpnd <- dplyr::select(bpnd, subject, Region, bp.logan.cer) #Keep only BPND values using logan with cerebellum as reference region
bpnd <- tidyr::spread(bpnd, Region, bp.logan.cer) #Convert table to tidy format
bpnd <- dplyr::select(bpnd, subject, LFC, THA, ACC, HIP, TC) #Keep only regions of interest
bpnd <- dplyr::rename(bpnd, DLPFC = LFC) #Change column name LFC to DLPFC for clarity

#Load Cognition file
cognition <- read_excel("/Users/marialee/ownCloud/FLB457_psychosis/DerivedData/Cognition/tidy_cognition.xlsx")

#Load Executive function file
wcst <- read_excel("/Users/marialee/ownCloud/FLB457_psychosis/DerivedData/Cognition/wcst_tidy.xlsx")
#Code Patient variable as 0 = HC and 1 = Patient
wcst$Patient <- recode(wcst$Patient, Patient = "1", HC = "0")
wcst$Patient <- as.numeric(wcst$Patient)
#Make WCST file for follow-up, for exploratory analyses
wcst_fu <- dplyr::filter(wcst, Baseline_FU == "FU")
#Filter out only Baseline cases for main analyses
wcst <- dplyr::filter(wcst, Baseline_FU == "Base")

#Convert non-numeric columns to numeric
cognition$Fluency <- as.numeric(cognition$Fluency, na.rm = TRUE) 
cognition$WMS_III <- as.numeric(cognition$WMS_III, na.rm = TRUE)
cognition$LNS <- as.numeric(cognition$LNS, na.rm = TRUE)
cognition$Mazes <- as.numeric(cognition$Mazes, na.rm = TRUE)
cognition$BVMT_R <- as.numeric(cognition$BVMT_R, na.rm = TRUE)
cognition$CPT <- as.numeric(cognition$CPT, na.rm = TRUE)

#Flip TMT test scores so that higher values are better
cognition$TMT_f <- ((max(cognition$TMT) - cognition$TMT) + min(cognition$TMT))

#Make domain score Speed of Processing from TMT, BACS and Fluency, using raw scores
cognition <- cognition %>% mutate(SOP = (TMT_f + BACS + Fluency)/3)
#Make domain score Working Memory from WMS_III and LNS, using raw scores
cognition <- cognition %>% mutate(WM = (WMS_III + LNS)/2)
#Make neurocognitive domain score using SOP, WM, HVLT-R, Mazes, BVMT-R, CPT, using raw scores
cognition <- cognition %>% mutate(Neurocog = (SOP + WM + HVLT_R + Mazes + BVMT_R + CPT/6))

```


#Aim
Aim of the study... 

#Preparation
Association between age and performance on cognitive tests is well-docmented, hence the need for age-corrected cognitive test scores. The norms of the MCCB were derived from an American norming sample, which might not be applicable to Swedish conditions. As no Swedish norming of the MCCB exists, we will age-correct our cognitive data and use the residuals from those regressions models. 

```{r, echo=FALSE}
#Wrangling data to be able to handle NA:s when I add age-corrected residuals; the Vincent approach (row names)
cognition <- as.data.frame(cognition) #Making it a data.frame because it doesn't work with tibble
new_name <- cognition$KASP_id
cognition <- data.frame(cognition, row.names = new_name)

wcst <- as.data.frame(wcst)
new_name_wcst <- wcst$ClientID
wcst <- data.frame(wcst, row.names = new_name_wcst)

#Make a regression model and extract the residuals, using the whole client sample for better correction
#Verbal Learning
model_verblearn <- lm(formula = HVLT_R ~ Age, cognition) #Regression model
agecorr_verblearn_residuals <- model_verblearn$residuals #Extracting residuals
agecorr_verblearn_residuals <- data.frame(names(agecorr_verblearn_residuals), agecorr_verblearn_residuals)
#Making residuals into data.frame to be able to join together with cognition data.frame in next step
#Working Memory
model_wm <- lm(formula = WM ~ Age, cognition) 
agecorr_wm_residuals <- model_wm$residuals
agecorr_wm_residuals <- data.frame(names(agecorr_wm_residuals), agecorr_wm_residuals)
#Speed of Processing
model_sop <- lm(formula = SOP ~ Age, cognition) 
agecorr_sop_residuals <- model_sop$residuals
agecorr_sop_residuals <- data.frame(names(agecorr_sop_residuals), agecorr_sop_residuals)
#Visual Learning
model_vis_learn <- lm(formula = BVMT_R ~ Age, cognition) 
agecorr_vis_learn_residuals <- model_vis_learn$residuals
agecorr_vis_learn_residuals <- data.frame(names(agecorr_vis_learn_residuals), agecorr_vis_learn_residuals)
#Attention
model_cpt <- lm(formula = CPT ~ Age, cognition) 
agecorr_cpt_residuals <- model_cpt$residuals
agecorr_cpt_residuals <- data.frame(names(agecorr_cpt_residuals), agecorr_cpt_residuals)
#General Cognitive Ability
model_neuro_cog <- lm(formula = Neurocog ~ Age, cognition) 
agecorr_neuro_cog_residuals <- model_neuro_cog$residuals
agecorr_neuro_cog_residuals <- data.frame(names(agecorr_neuro_cog_residuals), agecorr_neuro_cog_residuals)
#Executive Function
model_wcst <- lm(formula = PctErrors ~ AgeYr, wcst)
agecorr_wcst_residuals <- model_wcst$residuals
agecorr_wcst_residuals <- data.frame(names(agecorr_wcst_residuals), agecorr_wcst_residuals)

#Add residuals to cognition data.frame, using full_join
cognition <- full_join(cognition, agecorr_verblearn_residuals, by = c("KASP_id" = "names.agecorr_verblearn_residuals."))
cognition <- full_join(cognition, agecorr_wm_residuals, by = c("KASP_id" = "names.agecorr_wm_residuals."))
cognition <- full_join(cognition, agecorr_sop_residuals, by = c("KASP_id" = "names.agecorr_sop_residuals."))
cognition <- full_join(cognition, agecorr_vis_learn_residuals, by = c("KASP_id" = "names.agecorr_vis_learn_residuals."))
cognition <- full_join(cognition, agecorr_cpt_residuals, by = c("KASP_id" = "names.agecorr_cpt_residuals."))
cognition <- full_join(cognition, agecorr_neuro_cog_residuals, by = c("KASP_id" = "names.agecorr_neuro_cog_residuals."))

#Executive Function 
wcst <- full_join(wcst, agecorr_wcst_residuals, by = c("ClientID" = "names.agecorr_wcst_residuals."))

```



```{r, echo=FALSE}

#Check match between residuals and cognition by plotting them against one another 

plot(cognition$agecorr_verblearn_residuals, cognition$HVLT_R, main = "Verbal Learning", ylab = "Raw scores verbal learning", xlab = "Age corrected residuals for verbal learning")

plot(cognition$agecorr_wm_residuals, cognition$WM, main = "Working Memory", ylab = "Raw scores working memory composite", xlab = "Age corrected residuals for working memory composite")

plot(cognition$agecorr_sop_residuals, cognition$SOP, main = "Speed of Processing", ylab = "Raw scores speed of processing composite", xlab = "Age corrected residuals for speed of processing composite")

#Check match between residuals and cognition by plotting them against one another 

plot(cognition$agecorr_vis_learn_residuals, cognition$BVMT_R, main = "Visual Learning", ylab = "Raw scores BVMT-R", xlab = "Age corrected residuals for visual learning")

plot(cognition$agecorr_cpt_residuals, cognition$CPT, main = "Attention", ylab = "Raw scores CPT", xlab = "Age corrected residuals for attention")

plot(cognition$agecorr_neuro_cog_residuals, cognition$Neurocog, main = "General Cognitive Ability", ylab = "Raw scores neurocognitive composite", xlab = "Age corrected residuals for general cognitive ability")

plot(wcst$agecorr_wcst_residuals, wcst$PctErrors, main = "Executive Function", ylab = "Raw scores Percentage Errors WCST", xlab = "Age corrected residuals for executive function")


```




```{r, echo=FALSE, include=FALSE}

#Standardizing the age-corrected residuals for more interpretable beta-estimates
cognition <- cognition %>% 
                  mutate_at(.vars = vars("agecorr_verblearn_residuals", "agecorr_wm_residuals", 
                                        "agecorr_sop_residuals", "agecorr_vis_learn_residuals", 
                                        "agecorr_cpt_residuals", "agecorr_neuro_cog_residuals"),
                            .funs = list(~scale(.) %>% as.vector))
wcst <- wcst %>% mutate_at(.vars = vars("agecorr_wcst_residuals"),
                           .funs = list(~scale(.)%>% as.vector))

#Merge PET dataset with Cognition dataset, for the PET subjects only
d2_cognition <- dplyr::inner_join(bpnd, cognition) #Cognition (MCCB) and PET subjects
d2_wcst <- dplyr::inner_join(bpnd, wcst) #Cognition (WCST) and PET subjects

#Make regression models and extract age-corrected BPND residuals to use in plots for more accurate depiction of linear models
#DLPFC
model_bp_dlpfc <- lm(formula = DLPFC ~ Age, d2_cognition)
agecorr_bpnd_dlpfc <- model_bp_dlpfc$residuals
#Hippocampus
model_bp_hip <- lm(formula = HIP ~ Age, d2_cognition) #BPND HIP
agecorr_bpnd_hip <- model_bp_hip$residuals
#Thalamus - add if needed
model_bp_tha <- lm(formula = THA ~ Age, d2_cognition)
agecorr_bpnd_tha <- model_bp_tha$residuals
#ACC - add if needed
model_bp_acc <- lm(formula = ACC ~ Age, d2_cognition)
agecorr_bpnd_acc <- model_bp_acc$residuals
#Temporal cortex - add if needed
model_bp_tc <- lm(formula = TC ~ Age, d2_cognition)
agecorr_bpnd_tc <- model_bp_tc$residuals

#Add to D2Cognition data.frame
d2_cognition$agecorr_bpnd_dlpfc <- agecorr_bpnd_dlpfc
d2_cognition$agecorr_bpnd_hip <- agecorr_bpnd_hip
d2_cognition$agecorr_bpnd_tha <- agecorr_bpnd_tha
d2_cognition$agecorr_bpnd_acc <- agecorr_bpnd_acc
d2_cognition$agecorr_bpnd_tc <- agecorr_bpnd_tc

#The above was not done for BPND values in the WCST data frame, as none of those exploratory analyses showed any promising trends worth plotting

#For regression models with interaction effect we want to center the values of our variables, except for the dummy variable HC_pat. 
#Center age and BPND values for interaction plots, then add to D2Cognition data.frame

#Center age variable for cognition data.frame
d2_cognition$Age_c <- scale(d2_cognition$Age, center = T, scale = F)
#Center BPND variables, for use in interaction analyses, cognition data.frame
d2_cognition$DLPFC_c <- scale(d2_cognition$DLPFC, center = T, scale = F)
d2_cognition$HIP_c <- scale(d2_cognition$HIP, center = T, scale = F)
d2_cognition$THA_c <- scale(d2_cognition$THA, center = T, scale = F)
d2_cognition$ACC_c <- scale(d2_cognition$ACC, center = T, scale = F)
d2_cognition$TC_c <- scale(d2_cognition$TC, center = T, scale = F)

#Center age variable for wcst data.frame
d2_wcst$AgeYr_c <- scale(d2_wcst$AgeYr, center = T, scale = F)
#Center BPND variables, for use in interaction analyses, wcst data.frame 
d2_wcst$DLPFC_c <- scale(d2_wcst$DLPFC, center = T, scale = F)
d2_wcst$HIP_c <- scale(d2_wcst$HIP, center = T, scale = F)
d2_wcst$THA_c <- scale(d2_wcst$THA, center = T, scale = F)
d2_wcst$ACC_c <- scale(d2_wcst$ACC, center = T, scale = F)
d2_wcst$TC_c <- scale(d2_wcst$TC, center = T, scale = F)

```



##  Confirmatory analysis part 1 - regression without interaction effect

```{r, echo=FALSE}

#Calculate the actual regression
#CONFIRMATORY ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
model_vl_dlpfc <- lm(formula = DLPFC ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition)
summary(model_vl_dlpfc)
round(confint(model_vl_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$DLPFC,d2_cognition$agecorr_verblearn_residuals, d2_cognition[,c("Age","Patient")])

#CONFIRMATORY ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
model_vl_hip <- lm(formula = HIP ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition)
summary(model_vl_hip)
round(confint(model_vl_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$HIP,d2_cognition$agecorr_verblearn_residuals, d2_cognition[,c("Age","Patient")])

#CONFIRMATORY ANALYSIS 3 - WORKING MEMORY AND D2R IN DLPFC
model_wm_dlpfc <- lm(formula = DLPFC ~ agecorr_wm_residuals + Age + Patient, data = d2_cognition)
summary(model_wm_dlpfc)
round(confint(model_wm_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$DLPFC,d2_cognition$agecorr_wm_residuals, d2_cognition[,c("Age","Patient")])

#CONFIRMATORY ANALYSIS 4 - SPEED OF PROCESSING AND D2R IN DLPFC
model_sop_dlpfc <- lm(formula = DLPFC ~ agecorr_sop_residuals + Age + Patient, data = d2_cognition)
summary(model_sop_dlpfc)
round(confint(model_sop_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$DLPFC,d2_cognition$agecorr_sop_residuals, d2_cognition[,c("Age","Patient")])

```

###  Correcting for multiple comparison

```{r}
#Checking inter-correlation between cognitive tests in confirmatory analyses, as well as between ROIs in these analyses
cor(d2_cognition$agecorr_verblearn_residuals, d2_cognition$agecorr_sop_residuals) #0.4580175, Verbal learning and Speed of Processing
cor(d2_cognition$agecorr_verblearn_residuals, d2_cognition$agecorr_wm_residuals) #0.2651436 Verbal learning and Working Memory
cor(d2_cognition$agecorr_sop_residuals, d2_cognition$agecorr_wm_residuals) #0.4965122 Speed of Processing and Working Memory

cor(d2_cognition$DLPFC, d2_cognition$HIP) #0.3544352, DLPFC and Hippocampus

#Computing the number of effective tests among all dependent variables in confirmatory analyses section, mEff, as described in Derringer, 2018, using the meff-function. 

#Downloading meff function
source('https://osf.io/ws6xc/download')
#Set alpha level
alpha <- 0.05
meff_bpnd <- meff(d2_cognition[, c("DLPFC", "HIP")])
#Calculating new p-value for hypothesis testing section. 
p_value <- alpha/meff_bpnd
p_value

```


Based on the Meff calculation the new p-value for the confirmatory analyses will be set to 0.027.


```{r}

#Plot the regression model and a single regression line
#First, make duplicate plot of first one to be able to extract legend from
conf_plot0 <- ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient), shape = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, color = "black") +
  scale_color_manual(name="", 
                     labels = c("HC", 
                                "FEP"),
                     values = c("0"="blue", 
                                "1"="red")) +
  scale_shape_manual(name="",
                     labels = c("HC",
                                "FEP"),
                                values = c(1, 17)) + 
  labs(x = "Verbal Learning", y = "DLPFC") +
  theme_minimal_grid() +
  panel_border()

#CONFIRMATORY ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
conf_plot1 <- ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient), shape = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, color = "black") +
  scale_color_manual(name="", 
                     labels = c("HC", 
                                "FEP"),
                     values = c("0"="blue", 
                                "1"="red")) +
  scale_shape_manual(values = c(1, 17)) + 
  ylim(-0.7, 0.7) +
  xlim(-1.6, 1.8) +
  theme_minimal_grid() +
  theme(legend.position="None") +
  labs(x = "Verbal Learning", y = "DLPFC") +
  panel_border()

#CONFIRMATORY ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
conf_plot2 <- ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = agecorr_bpnd_hip)) +
  geom_point(aes(colour = factor(Patient), shape = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, color = "black") +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  scale_shape_manual(values = c(1, 17)) + 
  ylim(-0.7, 0.7) +
  xlim(-1.6, 1.8) +
  theme_minimal_grid() +
  theme(legend.position="None") +
  labs(x = "Verbal Learning", y = "Hippocampus") +
  panel_border()

#CONFIRMATORY ANALYSIS 3 - WORKING MEMORY AND D2R IN DLPFC
conf_plot3 <- ggplot(d2_cognition, aes(x = agecorr_wm_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient), shape = factor(Patient), fill = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, color = "black") +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  scale_shape_manual(values = c(1, 17)) + 
  ylim(-0.7, 0.7) +
  xlim(-1.6, 1.8) +
  theme_minimal_grid() +
  theme(legend.position="None") +
  labs(x = "Working memory", y = "DLPFC") +
  panel_border()

#CONFIRMATORY ANALYSIS 4 - SPEED OF PROCESSING AND D2R IN DLPFC
conf_plot4 <- ggplot(d2_cognition, aes(x = agecorr_sop_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient), shape = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, color = "black") +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  scale_shape_manual(values = c(1, 17)) + 
  ylim(-0.7, 0.7) +
  xlim(-1.6, 1.8) +
  theme_minimal_grid() +
  theme(legend.position="None") +
  labs(x = "Speed of processing", y = "DLPFC") +
  panel_border()
  

plot_cube <- plot_grid(conf_plot1, conf_plot2, conf_plot3, conf_plot4, labels = c('a', 'b', 'c', 'd'))

#Adding patient/healthy control legend by extracting the legend from first plot
legend <- get_legend(
  conf_plot0 + 
    guides(color = guide_legend(nrow = 1, label = TRUE)) +
    theme(legend.position = "bottom", legend.justification = "center"))

#Adding a title
#title <- ggdraw() +
 # draw_label(
   # "Confirmatory analyses of D2-R levels and cognition",
  #  fontface = 'bold',
  #  x = 0,
  #  hjust = 0
  #) +
  #theme(
  #  # add margin on the left of the drawing canvas,
  #  # so title is aligned with left edge of first plot
   # plot.margin = margin(0, 0, 0, 7)
  #)

#Put title, legend and plot together and plot
plot_grid(
  plot_cube, legend,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(1, 0.2)
)

```

### Checking model assumptions
1) Verbal learning in the DLPFC
2) Verbal learning in the hippocampus
3) Working memory in the DLPFC
4) Speed of proccessing in the DLPFC


```{r}
#Verbal learning DLPFC
plot_vl_dlpfc <- plot(model_vl_dlpfc$fitted.values, model_vl_dlpfc$residuals)
par(mfrow = c(2,2))
plot(model_vl_dlpfc)

#Verbal learning hippocampus
plot_vl_hip <- plot(model_vl_hip$fitted.values, model_vl_hip$residuals)
par(mfrow = c(2,2))
plot(model_vl_hip)

#Working memory DLPFC
plot_wm_dlpfc <- plot(model_wm_dlpfc$fitted.values, model_wm_dlpfc$residuals)
par(mfrow = c(2,2))
plot(model_wm_dlpfc)

#Speed of processing DLPFC
plot_sop_dlpfc <- plot(model_sop_dlpfc$fitted.values, model_sop_dlpfc$residuals)
par(mfrow = c(2,2))
plot(model_sop_dlpfc)

```





##  Confirmatory analysis part 2 - with interaction effect for patients/healthy controls

```{r, echo=FALSE, include=TRUE}

#Calculate the regression model with interaction effect

#CONFIRMATORY ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
model_vl_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_verblearn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vl_dlpfc2_c)
round(confint(model_vl_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
d2_cognition_p <- dplyr::filter(d2_cognition, Patient == 1)
d2_cognition_h <- dplyr::filter(d2_cognition, Patient == 0)
pcor.test(d2_cognition_p$DLPFC,d2_cognition_p$agecorr_verblearn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$DLPFC,d2_cognition_h$agecorr_verblearn_residuals, d2_cognition_h[,c("Age")])

#CONFIRMATORY ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
model_vl_hip2_c <- lm(formula = HIP_c ~ agecorr_verblearn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vl_hip2_c)
round(confint(model_vl_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$HIP,d2_cognition_p$agecorr_verblearn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$HIP,d2_cognition_h$agecorr_verblearn_residuals, d2_cognition_h[,c("Age")])

#CONFIRMATORY ANALYSIS 3 - WORKING MEMORY AND D2R IN DLPFC
model_wm_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_wm_residuals*Patient + Age_c, data = d2_cognition)
summary(model_wm_dlpfc2_c)
round(confint(model_wm_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$DLPFC,d2_cognition_p$agecorr_wm_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$DLPFC,d2_cognition_h$agecorr_wm_residuals, d2_cognition_h[,c("Age")])

#CONFIRMATORY ANALYSIS 4 - SPEED OF PROCESSING AND D2R IN DLPFC
model_sop_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_sop_residuals*Patient + Age_c, data = d2_cognition)
summary(model_sop_dlpfc2_c)
round(confint(model_sop_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$DLPFC,d2_cognition_p$agecorr_sop_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$DLPFC,d2_cognition_h$agecorr_sop_residuals, d2_cognition_h[,c("Age")])

```



```{r}

#Plot the regression model and the regression lines for the two groups 

#First, make duplicate plot of first one to be able to extract legend from
conf_plot5 <- ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  labs(x = "Verbal Learning", y = "DLPFC")

#CONFIRMATORY ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
conf_plot6 <- ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  theme(legend.position="None") +
  labs(x = "Verbal Learning", y = "DLPFC")

#CONFIRMATORY ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
conf_plot7 <- ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = agecorr_bpnd_hip)) +
  geom_point(aes(colour = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  theme(legend.position="None") +
  labs(x = "Verbal Learning", y = "Hippocampus")

#CONFIRMATORY ANALYSIS 3 - WORKING MEMORY AND D2R IN DLPFC
conf_plot8 <- ggplot(d2_cognition, aes(x = agecorr_wm_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  theme(legend.position="None") +
  labs(x = "Working memory", y = "DLPFC")

#CONFIRMATORY ANALYSIS 4 - SPEED OF PROCESSING AND D2R IN DLPFC
conf_plot9 <- ggplot(d2_cognition, aes(x = agecorr_sop_residuals, y = agecorr_bpnd_dlpfc)) +
  geom_point(aes(colour = factor(Patient))) +
  geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
  scale_color_manual(name="", 
                     labels = c("Healthy control", 
                                "Patient"),
                     values = c("0"="blue", 
                                "1"="red")) +
  theme(legend.position="None") +
  labs(x = "Speed of processing", y = "DLPFC")

plot_cube2 <- plot_grid(conf_plot6, conf_plot7, conf_plot8, conf_plot9, labels = c('1', '2', '3', '4'))

#Adding patient/healthy control legend by extracting the legend from first plot
legend <- get_legend(
  conf_plot5 + 
    guides(color = guide_legend(nrow = 1, label = TRUE)) +
    theme(legend.position = "bottom"))

#Adding a title
title <- ggdraw() +
  draw_label(
    "Confirmatory analyses of D2-R levels and cognition",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

#Put title, legend and plot together and plot
plot_grid(
  title, plot_cube2, legend,
  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1, 0.1)
)



```

###  Checking model assumptions, with interaction effect.
1) Verbal learning in the DLPFC
2) Verbal learning in the hippocampus
3) Working memory in the DLPFC
4) Speed of proccessing in the DLPFC

```{r}

#Verbal learning DLPFC
plot_vl_dlpfc2_c <- plot(model_vl_dlpfc2_c$fitted.values, model_vl_dlpfc2_c$residuals)
par(mfrow = c(2,2))
plot(model_vl_dlpfc2_c)

#Verbal learning hippocampus
plot_vl_hip2_c <- plot(model_vl_hip2_c$fitted.values, model_vl_hip2_c$residuals)
par(mfrow = c(2,2))
plot(model_vl_hip2_c)

#Working memory DLPFC
plot_wm_dlpfc2_c <- plot(model_wm_dlpfc2_c$fitted.values, model_wm_dlpfc2_c$residuals)
par(mfrow = c(2,2))
plot(model_wm_dlpfc2_c)

#Speed of processing DLPFC
plot_sop_dlpfc2_c <- plot(model_sop_dlpfc2_c$fitted.values, model_sop_dlpfc2_c$residuals)
par(mfrow = c(2,2))
plot(model_sop_dlpfc2_c)


```


###  Table of the residuals 


```{r}
#EXPLORATORY ANALYSES

#EV helt onödigt?

#Make data.frame to look at the min, max, range, mean and sd of residuals
min <- c(min(model_verblearn$residuals), min(model_wm$residuals), min(model_sop$residuals), min(model_vis_learn$residuals), min(model_cpt$residuals), min(model_neuro_cog$residuals), min(model_wcst$residuals))

max <- c(max(model_verblearn$residuals), max(model_wm$residuals), max(model_sop$residuals), max(model_vis_learn$residuals), max(model_cpt$residuals), max(model_neuro_cog$residuals), max(model_wcst$residuals))

mean <- c(mean(model_verblearn$residuals), mean(model_wm$residuals), mean(model_sop$residuals), mean(model_vis_learn$residuals), mean(model_cpt$residuals), mean(model_neuro_cog$residuals), mean(model_wcst$residuals))

sd <- c(sd(model_verblearn$residuals), sd(model_wm$residuals), sd(model_sop$residuals), sd(model_vis_learn$residuals), sd(model_cpt$residuals), sd(model_neuro_cog$residuals), sd(model_wcst$residuals))

min <- round(min, digits = 3)
max <- round(max, digits = 3)
mean <- round(mean, digits = 3)
sd <- round(sd, digits = 3)

resid.frame <- data.frame(min, max, mean, sd)
rownames(resid.frame) <- c("Verbal learning", "Working Memory", "Speed of Processing", "Visual Learning", "Attention", "General Cognitive Ability", "Executive Function")

resid.frame

```


## Exploratory analysis part 1 - without interaction effect


```{r, echo=FALSE, include=TRUE}
#EXPLORATORY ANALYSIS 1 - VERBAL LEARNING AND D2R IN THALAMUS

model_verblearn_tha <- lm(formula = THA ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition)
summary(model_verblearn_tha)
round(confint(model_verblearn_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$THA,d2_cognition$agecorr_verblearn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 2 - VERBAL LEARNING AND D2R IN ACC
model_verblearn_acc <- lm(formula = ACC ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition)
summary(model_verblearn_acc)
round(confint(model_verblearn_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$ACC,d2_cognition$agecorr_verblearn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 3 - VERBAL LEARNING AND D2R IN TC
model_verblearn_tc <- lm(formula = TC ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition)
summary(model_verblearn_tc)
round(confint(model_verblearn_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$TC,d2_cognition$agecorr_verblearn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 4 - ATTENTION AND D2R IN DLPFC
model_cpt_dlpfc <- lm(formula = DLPFC ~ agecorr_cpt_residuals + Age + Patient, data = d2_cognition)
summary(model_cpt_dlpfc)
round(confint(model_cpt_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$DLPFC,d2_cognition$agecorr_cpt_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 5 - ATTENTION AND D2R IN THA
model_cpt_tha <- lm(formula = THA ~ agecorr_cpt_residuals + Age + Patient, data = d2_cognition)
summary(model_cpt_tha)
round(confint(model_cpt_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$THA,d2_cognition$agecorr_cpt_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 5 - ATTENTION AND D2R IN ACC
model_cpt_acc <- lm(formula = ACC ~ agecorr_cpt_residuals + Age + Patient, data = d2_cognition)
summary(model_cpt_acc)
round(confint(model_cpt_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$ACC,d2_cognition$agecorr_cpt_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 6 - ATTENTION AND D2R IN HIP
model_cpt_hip <- lm(formula = HIP ~ agecorr_cpt_residuals + Age + Patient, data = d2_cognition)
summary(model_cpt_hip)
round(confint(model_cpt_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$HIP,d2_cognition$agecorr_cpt_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 7 - ATTENTION AND D2R IN TC
model_cpt_tc <- lm(formula = TC ~ agecorr_cpt_residuals + Age + Patient, data = d2_cognition)
summary(model_cpt_tc)
round(confint(model_cpt_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$TC,d2_cognition$agecorr_cpt_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 8 - WORKING MEMORY AND D2R IN THA
model_wm_tha <- lm(formula = THA ~ agecorr_wm_residuals + Age + Patient, data = d2_cognition)
summary(model_wm_tha)
round(confint(model_wm_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$THA,d2_cognition$agecorr_wm_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 9 - WORKING MEMORY AND D2R IN ACC
model_wm_acc <- lm(formula = ACC ~ agecorr_wm_residuals + Age + Patient, data = d2_cognition)
summary(model_wm_acc)
round(confint(model_wm_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$ACC,d2_cognition$agecorr_wm_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 10 - WORKING MEMORY AND D2R IN HIP
model_wm_hip <- lm(formula = HIP ~ agecorr_wm_residuals + Age + Patient, data = d2_cognition)
summary(model_wm_hip)
round(confint(model_wm_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$HIP,d2_cognition$agecorr_wm_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 11 - WORKING MEMORY AND D2R IN TC
model_wm_tc <- lm(formula = TC ~ agecorr_wm_residuals + Age + Patient, data = d2_cognition)
summary(model_wm_tc)
round(confint(model_wm_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$TC,d2_cognition$agecorr_wm_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 12 - VISUAL LEARNING AND D2R IN DLPFC
model_vis_learn_dlpfc <- lm(formula = DLPFC ~ agecorr_vis_learn_residuals + Age + Patient, data = d2_cognition)
summary(model_vis_learn_dlpfc)
round(confint(model_vis_learn_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$DLPFC,d2_cognition$agecorr_vis_learn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 13 - VISUAL LEARNING AND D2R IN THA
model_vis_learn_tha <- lm(formula = THA ~ agecorr_vis_learn_residuals + Age + Patient, data = d2_cognition)
summary(model_vis_learn_tha)
round(confint(model_vis_learn_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$THA,d2_cognition$agecorr_vis_learn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 14 - VISUAL LEARNING AND D2R IN ACC
model_vis_learn_acc <- lm(formula = ACC ~ agecorr_vis_learn_residuals + Age + Patient, data = d2_cognition)
summary(model_vis_learn_acc)
round(confint(model_vis_learn_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$ACC,d2_cognition$agecorr_vis_learn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 15 - VISUAL LEARNING AND D2R IN HIP
model_vis_learn_hip <- lm(formula = HIP ~ agecorr_vis_learn_residuals + Age + Patient, data = d2_cognition)
summary(model_vis_learn_hip)
round(confint(model_vis_learn_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$HIP,d2_cognition$agecorr_vis_learn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 16 - VISUAL LEARNING AND D2R IN TC
model_vis_learn_tc <- lm(formula = TC ~ agecorr_vis_learn_residuals + Age + Patient, data = d2_cognition)
summary(model_vis_learn_tc)
round(confint(model_vis_learn_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$TC,d2_cognition$agecorr_vis_learn_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 17 - SPEED OF PROCESSING AND D2R IN HIP
model_sop_hip <- lm(formula = HIP ~ agecorr_sop_residuals + Age + Patient, data = d2_cognition)
summary(model_sop_hip)
round(confint(model_sop_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$HIP,d2_cognition$agecorr_sop_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 18 - SPEED OF PROCESSING AND D2R IN THA
model_sop_tha <- lm(formula = THA ~ agecorr_sop_residuals + Age + Patient, data = d2_cognition)
summary(model_sop_tha)
round(confint(model_sop_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$THA,d2_cognition$agecorr_sop_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 19 - SPEED OF PROCESSING AND D2R IN ACC
model_sop_acc <- lm(formula = ACC ~ agecorr_sop_residuals + Age + Patient, data = d2_cognition)
summary(model_sop_acc)
round(confint(model_sop_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$ACC,d2_cognition$agecorr_sop_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 20 - SPEED OF PROCESSING AND D2R IN TC
model_sop_tc <- lm(formula = TC ~ agecorr_sop_residuals + Age + Patient, data = d2_cognition)
summary(model_sop_tc)
round(confint(model_sop_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$TC,d2_cognition$agecorr_sop_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 21 - EXECUTIVE FUNCTION AND D2R IN DLPFC
model_wcst_dlpfc <- lm(formula = DLPFC ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
summary(model_wcst_dlpfc)
round(confint(model_wcst_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_wcst$DLPFC,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 22 - EXECUTIVE FUNCTION AND D2R IN HIP
model_wcst_hip <- lm(formula = HIP ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
summary(model_wcst_hip)
round(confint(model_wcst_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_wcst$HIP,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 23 - EXECUTIVE FUNCTION AND D2R IN THA
model_wcst_tha <- lm(formula = THA ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
summary(model_wcst_tha)
round(confint(model_wcst_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_wcst$THA,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 24 - EXECUTIVE FUNCTION AND D2R IN ACC
model_wcst_acc <- lm(formula = ACC ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
summary(model_wcst_acc)
round(confint(model_wcst_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_wcst$ACC,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 25 - EXECUTIVE FUNCTION AND D2R IN TC
model_wcst_tc <- lm(formula = TC ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
summary(model_wcst_tc)
round(confint(model_wcst_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_wcst$TC,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 26 - GENERAL COGNITIVE ABILITY AND D2R IN DLPFC
model_neuro_cog_dlpfc <- lm(formula = DLPFC ~ agecorr_neuro_cog_residuals + Age + Patient, data = d2_cognition)
summary(model_neuro_cog_dlpfc)
round(confint(model_neuro_cog_dlpfc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$DLPFC,d2_cognition$agecorr_neuro_cog_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 27 - GENERAL COGNITIVE ABILITY AND D2R IN HIP
model_neuro_cog_hip <- lm(formula = HIP ~ agecorr_neuro_cog_residuals + Age + Patient, data = d2_cognition)
summary(model_neuro_cog_hip)
round(confint(model_neuro_cog_hip), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$HIP,d2_cognition$agecorr_neuro_cog_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 28 - GENERAL COGNITIVE ABILITY AND D2R IN THA
model_neuro_cog_tha <- lm(formula = THA ~ agecorr_neuro_cog_residuals + Age + Patient, data = d2_cognition)
summary(model_neuro_cog_tha)
round(confint(model_neuro_cog_tha), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$THA,d2_cognition$agecorr_neuro_cog_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 29 - GENERAL COGNITIVE ABILITY AND D2R IN ACC
model_neuro_cog_acc <- lm(formula = ACC ~ agecorr_neuro_cog_residuals + Age + Patient, data = d2_cognition)
summary(model_neuro_cog_acc)
round(confint(model_neuro_cog_acc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$ACC,d2_cognition$agecorr_neuro_cog_residuals, d2_cognition[,c("Age","Patient")])

#EXPLORATORY ANALYSIS 30 - GENERAL COGNITIVE ABILITY AND D2R IN TC
model_neuro_cog_tc <- lm(formula = TC ~ agecorr_neuro_cog_residuals + Age + Patient, data = d2_cognition)
summary(model_neuro_cog_tc)
round(confint(model_neuro_cog_tc), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cognition$TC,d2_cognition$agecorr_neuro_cog_residuals, d2_cognition[,c("Age","Patient")])

```


##  Graphs of exploratory analyses with low p-values and high partial r-values



```{r}

#EXPLORATORY ANALYSIS 3 - VERBAL LEARNING AND D2R IN TC
ggplot(d2_cognition, aes(x = agecorr_verblearn_residuals, y = TC)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
labs(x = "Verbal learning", y = "D2R BPND Temporal cortex", title = "Association between dopamine D2 receptor density in Temporal cortex and verbal learning")

#EXPLORATORY ANALYSIS 5 - ATTENTION AND D2R IN THA
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = THA)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
labs(x = "Attention", y = "D2R BPND Thalamus", title = "Association between dopamine D2 receptor density in Thalamus and attention")

#EXPLORATORY ANALYSIS 5 - ATTENTION AND D2R IN ACC
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = ACC)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
labs(x = "Attention", y = "D2R BPND ACC", title = "Association between dopamine D2 receptor density in ACC and attention")

#EXPLORATORY ANALYSIS 6 - ATTENTION AND D2R IN HIP
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = HIP)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
labs(x = "Attention", y = "D2R BPND Hippocampus", title = "Association between dopamine D2 receptor density in Hippocampus and attention")

#EXPLORATORY ANALYSIS 7 - ATTENTION AND D2R IN TC
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = TC)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient, color = factor(Patient))) +
labs(x = "Attention", y = "D2R BPND Temporal cortex", title = "Association between dopamine D2 receptor density in temporal cortex and attention")



```




```{r, echo=FALSE, include=TRUE}
#Calculate the regression model with interaction effect 

#EXPLORATORY ANALYSIS 31 - VERBAL LEARNING AND D2R IN THALAMUS - INTERACTION
model_verblearn_tha2_c <- lm(formula = THA_c ~ agecorr_verblearn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_verblearn_tha2_c)
round(confint(model_verblearn_tha2_c), digits = 3)
#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$THA,d2_cognition_p$agecorr_verblearn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$THA,d2_cognition_h$agecorr_verblearn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 32 - VERBAL LEARNING AND D2R IN ACC - INTERACTION
model_verblearn_acc2_c <- lm(formula = ACC_c ~ agecorr_verblearn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_verblearn_acc2_c)
round(confint(model_verblearn_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$ACC,d2_cognition_p$agecorr_verblearn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$ACC,d2_cognition_h$agecorr_verblearn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 33 - VERBAL LEARNING AND D2R IN TC - INTERACTION
model_verblearn_tc2_c <- lm(formula = TC_c ~ agecorr_verblearn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_verblearn_tc2_c)
round(confint(model_verblearn_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$TC,d2_cognition_p$agecorr_verblearn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$TC,d2_cognition_h$agecorr_verblearn_residuals, d2_cognition_h[,c("Age")])

#CONFIRMATORY ANALYSIS - VERBAL LEARNING AND D2R IN DLPFC/HIPPOCAMPUS

#EXPLORATORY ANALYSIS 34 - ATTENTION AND D2R IN DLPFC - INTERACTION
#Center attention? 
model_cpt_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_cpt_residuals*Patient + Age_c, data = d2_cognition)
summary(model_cpt_dlpfc2_c)
round(confint(model_cpt_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$DLPFC,d2_cognition_p$agecorr_cpt_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$DLPFC,d2_cognition_h$agecorr_cpt_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 35 - ATTENTION AND D2R IN THA - INTERACTION
model_cpt_tha2_c <- lm(formula = THA_c ~ agecorr_cpt_residuals*Patient + Age_c, data = d2_cognition)
summary(model_cpt_tha2_c)
round(confint(model_cpt_tha2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$THA,d2_cognition_p$agecorr_cpt_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$THA,d2_cognition_h$agecorr_cpt_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 36 - ATTENTION AND D2R IN ACC - INTERACTION
model_cpt_acc2_c <- lm(formula = ACC_c ~ agecorr_cpt_residuals*Patient + Age_c, data = d2_cognition)
summary(model_cpt_acc2_c)
round(confint(model_cpt_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$ACC,d2_cognition_p$agecorr_cpt_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$ACC,d2_cognition_h$agecorr_cpt_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 37 - ATTENTION AND D2R IN HIP - INTERACTION
model_cpt_hip2_c <- lm(formula = HIP_c ~ agecorr_cpt_residuals*Patient + Age_c, data = d2_cognition)
summary(model_cpt_hip2_c)
round(confint(model_cpt_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$HIP,d2_cognition_p$agecorr_cpt_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$HIP,d2_cognition_h$agecorr_cpt_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 38 - ATTENTION AND D2R IN TC - INTERACTION
model_cpt_tc2_c <- lm(formula = TC_c ~ agecorr_cpt_residuals*Patient + Age_c, data = d2_cognition)
summary(model_cpt_tc2_c)
round(confint(model_cpt_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$TC,d2_cognition_p$agecorr_cpt_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$TC,d2_cognition_h$agecorr_cpt_residuals, d2_cognition_h[,c("Age")])

#CONFIRMATORY ANALYSIS - WORKING MEMORY AND D2R IN DLPFC

#EXPLORATORY ANALYSIS 39 - WORKING MEMORY AND D2R IN THA - INTERACTION
#Center working memory?
model_wm_tha2_c <- lm(formula = THA_c ~ agecorr_wm_residuals*Patient + Age_c, data = d2_cognition)
summary(model_wm_tha2_c)
round(confint(model_wm_tha2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$THA,d2_cognition_p$agecorr_wm_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$THA,d2_cognition_h$agecorr_wm_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 40 - WORKING MEMORY AND D2R IN ACC - INTERACTION
model_wm_acc2_c <- lm(formula = ACC_c ~ agecorr_wm_residuals*Patient + Age_c, data = d2_cognition)
summary(model_wm_acc2_c)
round(confint(model_wm_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$ACC,d2_cognition_p$agecorr_wm_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$ACC,d2_cognition_h$agecorr_wm_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 41 - WORKING MEMORY AND D2R IN HIP - INTERACTION
model_wm_hip2_c <- lm(formula = HIP_c ~ agecorr_wm_residuals*Patient + Age_c, data = d2_cognition)
summary(model_wm_hip2_c)
round(confint(model_wm_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$HIP,d2_cognition_p$agecorr_wm_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$HIP,d2_cognition_h$agecorr_wm_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 42 - WORKING MEMORY AND D2R IN TC - INTERACTION
model_wm_tc2_c <- lm(formula = TC_c ~ agecorr_wm_residuals*Patient + Age_c, data = d2_cognition)
summary(model_wm_tc2_c)
round(confint(model_wm_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$TC,d2_cognition_p$agecorr_wm_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$TC,d2_cognition_h$agecorr_wm_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 43 - VISUAL LEARNING AND D2R IN DLPFC - INTERACTION
#Center visual learning?
model_vis_learn_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_vis_learn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vis_learn_dlpfc2_c)
round(confint(model_vis_learn_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$DLPFC,d2_cognition_p$agecorr_vis_learn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$DLPFC,d2_cognition_h$agecorr_vis_learn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 44 - VISUAL LEARNING AND D2R IN THA - INTERACTION
model_vis_learn_tha2_c <- lm(formula = THA_c ~ agecorr_vis_learn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vis_learn_tha2_c)
round(confint(model_vis_learn_tha2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$THA,d2_cognition_p$agecorr_vis_learn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$THA,d2_cognition_h$agecorr_vis_learn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 45 - VISUAL LEARNING AND D2R IN ACC - INTERACTION
model_vis_learn_acc2_c <- lm(formula = ACC_c ~ agecorr_vis_learn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vis_learn_acc2_c)
round(confint(model_vis_learn_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$ACC,d2_cognition_p$agecorr_vis_learn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$ACC,d2_cognition_h$agecorr_vis_learn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 46 - VISUAL LEARNING AND D2R IN HIP - INTERACTION
model_vis_learn_hip2_c <- lm(formula = HIP_c ~ agecorr_vis_learn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vis_learn_hip2_c)
round(confint(model_vis_learn_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$HIP,d2_cognition_p$agecorr_vis_learn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$HIP,d2_cognition_h$agecorr_vis_learn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 47 - VISUAL LEARNING AND D2R IN TC - INTERACTION
model_vis_learn_tc2_c <- lm(formula = TC_c ~ agecorr_vis_learn_residuals*Patient + Age_c, data = d2_cognition)
summary(model_vis_learn_tc2_c)
round(confint(model_vis_learn_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$TC,d2_cognition_p$agecorr_vis_learn_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$TC,d2_cognition_h$agecorr_vis_learn_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 48 - SPEED OF PROCESSING AND D2R IN HIP - INTERACTION
#Center speed of processing?
model_sop_hip2_c <- lm(formula = HIP_c ~ agecorr_sop_residuals*Patient + Age_c, data = d2_cognition)
summary(model_sop_hip2_c)
round(confint(model_sop_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$HIP,d2_cognition_p$agecorr_sop_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$HIP,d2_cognition_h$agecorr_sop_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 49 - SPEED OF PROCESSING AND D2R IN THA - INTERACTION
model_sop_tha2_c <- lm(formula = THA_c ~ agecorr_sop_residuals*Patient + Age_c, data = d2_cognition)
summary(model_sop_tha2_c)
round(confint(model_sop_tha2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$THA,d2_cognition_p$agecorr_sop_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$THA,d2_cognition_h$agecorr_sop_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 50 - SPEED OF PROCESSING AND D2R IN ACC - INTERACTION
model_sop_acc2_c <- lm(formula = ACC_c ~ agecorr_sop_residuals*Patient + Age_c, data = d2_cognition)
summary(model_sop_acc2_c)
round(confint(model_sop_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$ACC,d2_cognition_p$agecorr_sop_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$ACC,d2_cognition_h$agecorr_sop_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 51 - SPEED OF PROCESSING AND D2R IN TC - INTERACTION
model_sop_tc2_c <- lm(formula = TC_c ~ agecorr_sop_residuals*Patient + Age_c, data = d2_cognition)
summary(model_sop_tc2_c)
round(confint(model_sop_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$TC,d2_cognition_p$agecorr_sop_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$TC,d2_cognition_h$agecorr_sop_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 52 - EXECUTIVE FUNCTION AND D2R IN DLPFC - INTERACTION
#Center executive function? 

model_wcst_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_wcst_residuals*Patient + AgeYr_c, data = d2_wcst) 
summary(model_wcst_dlpfc2_c)
round(confint(model_wcst_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
d2_wcst_p <- dplyr::filter(d2_wcst, Patient == 1)
d2_wcst_h <- dplyr::filter(d2_wcst, Patient == 0)
pcor.test(d2_wcst_p$DLPFC,d2_wcst_p$agecorr_wcst_residuals, d2_wcst_p[,c("AgeYr")])
pcor.test(d2_wcst_h$DLPFC,d2_wcst_h$agecorr_wcst_residuals, d2_wcst_h[,c("AgeYr")])

#EXPLORATORY ANALYSIS 53 - EXECUTIVE FUNCTION AND D2R IN HIP - INTERACTION
model_wcst_hip2_c <- lm(formula = HIP_c ~ agecorr_wcst_residuals*Patient + AgeYr_c, data = d2_wcst)
summary(model_wcst_hip2_c)
round(confint(model_wcst_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_wcst_p$HIP,d2_wcst_p$agecorr_wcst_residuals, d2_wcst_p[,c("AgeYr")])
pcor.test(d2_wcst_h$HIP,d2_wcst_h$agecorr_wcst_residuals, d2_wcst_h[,c("AgeYr")])

#EXPLORATORY ANALYSIS 54 - EXECUTIVE FUNCTION AND D2R IN THA - INTERACTION
model_wcst_tha2_c <- lm(formula = THA_c ~ agecorr_wcst_residuals*Patient + AgeYr_c, data = d2_wcst)
summary(model_wcst_tha2_c)
round(confint(model_wcst_tha2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_wcst_p$THA,d2_wcst_p$agecorr_wcst_residuals, d2_wcst_p[,c("AgeYr")])
pcor.test(d2_wcst_h$THA,d2_wcst_h$agecorr_wcst_residuals, d2_wcst_h[,c("AgeYr")])

#EXPLORATORY ANALYSIS 55 - EXECUTIVE FUNCTION AND D2R IN ACC - INTERACTION
model_wcst_acc2_c <- lm(formula = ACC_c ~ agecorr_wcst_residuals*Patient + AgeYr_c, data = d2_wcst)
summary(model_wcst_acc2_c)
round(confint(model_wcst_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_wcst_p$ACC,d2_wcst_p$agecorr_wcst_residuals, d2_wcst_p[,c("AgeYr")])
pcor.test(d2_wcst_h$ACC,d2_wcst_h$agecorr_wcst_residuals, d2_wcst_h[,c("AgeYr")])

#EXPLORATORY ANALYSIS 56 - EXECUTIVE FUNCTION AND D2R IN TC - INTERACTION
model_wcst_tc2_c <- lm(formula = TC_c ~ agecorr_wcst_residuals*Patient + AgeYr_c, data = d2_wcst)
summary(model_wcst_tc2_c)
round(confint(model_wcst_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_wcst_p$TC,d2_wcst_p$agecorr_wcst_residuals, d2_wcst_p[,c("AgeYr")])
pcor.test(d2_wcst_h$TC,d2_wcst_h$agecorr_wcst_residuals, d2_wcst_h[,c("AgeYr")])

#EXPLORATORY ANALYSIS 57 - GENERAL COGNITIVE ABILITY AND D2R IN DLPFC - INTERACTION
#Center general cognitive ability? 
model_neuro_cog_dlpfc2_c <- lm(formula = DLPFC_c ~ agecorr_neuro_cog_residuals*Patient + Age_c, data = d2_cognition)
summary(model_neuro_cog_dlpfc2_c)
round(confint(model_neuro_cog_dlpfc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$DLPFC,d2_cognition_p$agecorr_neuro_cog_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$DLPFC,d2_cognition_h$agecorr_neuro_cog_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 58 - GENERAL COGNITIVE ABILITY AND D2R IN HIP - INTERACTION
model_neuro_cog_hip2_c <- lm(formula = HIP_c ~ agecorr_neuro_cog_residuals*Patient + Age_c, data = d2_cognition)
summary(model_neuro_cog_hip2_c)
round(confint(model_neuro_cog_hip2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$HIP,d2_cognition_p$agecorr_neuro_cog_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$HIP,d2_cognition_h$agecorr_neuro_cog_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 59 - GENERAL COGNITIVE ABILITY AND D2R IN THA - INTERACTION
model_neuro_cog_tha2_c <- lm(formula = THA_c ~ agecorr_neuro_cog_residuals*Patient + Age_c, data = d2_cognition)
summary(model_neuro_cog_tha2_c)
round(confint(model_neuro_cog_tha2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$THA,d2_cognition_p$agecorr_neuro_cog_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$THA,d2_cognition_h$agecorr_neuro_cog_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 60 - GENERAL COGNITIVE ABILITY AND D2R IN ACC - INTERACTION
model_neuro_cog_acc2_c <- lm(formula = ACC_c ~ agecorr_neuro_cog_residuals*Patient + Age_c, data = d2_cognition)
summary(model_neuro_cog_acc2_c)
round(confint(model_neuro_cog_acc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$ACC,d2_cognition_p$agecorr_neuro_cog_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$ACC,d2_cognition_h$agecorr_neuro_cog_residuals, d2_cognition_h[,c("Age")])

#EXPLORATORY ANALYSIS 61 - GENERAL COGNITIVE ABILITY AND D2R IN TC - INTERACTION
model_neuro_cog_tc2_c <- lm(formula = TC_c ~ agecorr_neuro_cog_residuals*Patient + Age_c, data = d2_cognition)
summary(model_neuro_cog_tc2_c)
round(confint(model_neuro_cog_tc2_c), digits = 3)

#Partial r for patients and HC separately 
pcor.test(d2_cognition_p$TC,d2_cognition_p$agecorr_neuro_cog_residuals, d2_cognition_p[,c("Age")])
pcor.test(d2_cognition_h$TC,d2_cognition_h$agecorr_neuro_cog_residuals, d2_cognition_h[,c("Age")])

```

##  Graphs of exploratory analyses with low interaction effect and low p-values 


```{r}

#Plot the regression model and the regression lines for the two groups 

#EXPLORATORY ANALYSIS 35 - ATTENTION AND D2R IN THA - INTERACTION
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = agecorr_bpnd_tha)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient)) +
labs(x = "Attention", y = "D2R BPND Thalamus", title = "Association between dopamine D2 receptor density in Thalamus and attention")

#EXPLORATORY ANALYSIS 37 - ATTENTION AND D2R IN HIP - INTERACTION
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = agecorr_bpnd_hip)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient)) +
labs(x = "Attention", y = "D2R BPND Hippocampus", title = "Association between dopamine D2 receptor density in Hippocampus and attention")

#EXPLORATORY ANALYSIS 38 - ATTENTION AND D2R IN TC - INTERACTION
ggplot(d2_cognition, aes(x = agecorr_cpt_residuals, y = agecorr_bpnd_tc)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient)) +
labs(x = "Attention", y = "D2R BPND Temporal cortex", title = "Association between dopamine D2 receptor density in temporal cortex and attention")

#EXPLORATORY ANALYSIS 46 - VISUAL LEARNING AND D2R IN HIP - INTERACTION
ggplot(d2_cognition, aes(x = agecorr_vis_learn_residuals, y = agecorr_bpnd_hip)) +
geom_point(aes(colour = factor(Patient))) +
geom_smooth(method = "lm", se = TRUE, size = 0.5, aes(group = Patient)) +
labs(x = "Visual Learning", y = "D2R BPND Hippocampus", title = "Association between dopamine D2 receptor density in Hippocampus and visual learning")

```

##  Bayes Factor   


```{r, eval=FALSE, echo=FALSE}

#BAYES FACTOR
#BAYESIAN ANALYSIS
library(brms)
#First, prior for alternative hypothesis 
prior1 <- prior(normal(0, 0.5), class = "b", coef = "agecorr_verblearn_residuals")
prior2 <- prior(normal(0, 0.5), class = "b", coef = "agecorr_wm_residuals")
prior3 <- prior(normal(0, 0.5), class = "b", coef = "agecorr_sop_residuals")

#CONFIRMATORY ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
#Bayesian regression models. First, alternative hypothesis containing Cognitive variable
bayes_vl_dlpfc1 <- brm(formula = DLPFC ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition, family = gaussian, prior = prior1, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)

#Second, null-hypothesis without Cognitive variable 
bayes_vl_dlpfc0 <- brm(formula = DLPFC ~ Age + Patient, data = d2_cognition, family = gaussian, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)

#Plot diagnostics of sampling
plot(bayes_vl_dlpfc1)
plot(bayes_vl_dlpfc0)

#Summarize models
summary(bayes_vl_dlpfc1)
summary(bayes_vl_dlpfc0)

#Calculate Bayes Factor
#Estimated Bayes Factor in favor of bayes_vl_dlpfc1 over bayes_vl_dlpfc0:
BF10_vl_dlpfc <- bayes_factor(bayes_vl_dlpfc1, bayes_vl_dlpfc0) 
#To get BF0/1, divide 1 by the above BF
BF01_vl_dlpfc <- 1/BF10_vl_dlpfc$bf

#CONFIRMATORY ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
#Using same prior, as we are using the same cognitive test
#First, alternative hypothesis containing Cognitive variable
bayes_vl_hip1 <- brm(formula = HIP ~ agecorr_verblearn_residuals + Age + Patient, data = d2_cognition, family = gaussian, prior = prior1, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)
#Second, null-hypothesis without Cognitive variable
bayes_vl_hip0 <- brm(formula = HIP ~ Age + Patient, data = d2_cognition, family = gaussian, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)

#Plot diagnostics of sampling
plot(bayes_vl_hip1)
plot(bayes_vl_hip0)

#Summarize models
summary(bayes_vl_hip1)
summary(bayes_vl_hip0)

#Calculate Bayes Factor
#Estimated Bayes factor in favor of bayes_vl_dlpfc1 over bayes_vl_dlpfc0:
BF10_vl_hip <- bayes_factor(bayes_vl_hip1, bayes_vl_hip0) 
#To get BF0/1, divide 1 by the above BF
BF01_vl_hip <- 1/BF10_vl_hip$bf

#CONFIRMATORY ANALYSIS 3 - WORKING MEMORY AND D2R IN DLPFC
#Using prior2
#First, alternative hypothesis containing Cognitive variable
bayes_wm_dlpfc1 <- brm(formula = DLPFC ~ agecorr_wm_residuals + Age + Patient, data = d2_cognition, family = gaussian, prior = prior2, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)
#Second, null-hypothesis without Cognitive variable
bayes_wm_dlpfc0 <- brm(formula = DLPFC ~ Age + Patient, data = d2_cognition, family = gaussian, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)

#Plot diagnostics of sampling
plot(bayes_wm_dlpfc1)
plot(bayes_wm_dlpfc0)

#Summarize models
summary(bayes_wm_dlpfc1)
summary(bayes_wm_dlpfc0)

#Calculate Bayes Factor
#Estimated Bayes factor in favor of bayes_vl_dlpfc1 over bayes_vl_dlpfc0:
BF10_wm_dlpfc <- bayes_factor(bayes_wm_dlpfc1, bayes_wm_dlpfc0) 
#To get BF0/1, divide 1 by the above BF
BF01_wm_dlpfc <- 1/BF10_wm_dlpfc$bf

#Using prior 3
#CONFIRMATORY ANALYSIS 4 - SPEED OF PROCESSING AND D2R IN DLPFC
#First, alternative hypothesis containing Cognitive variable
bayes_sop_dlpfc1 <- brm(formula = DLPFC ~ agecorr_sop_residuals + Age + Patient, data = d2_cognition, family = gaussian, prior = prior3, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)
#Second, null-hypothesis without Cognitive variable
bayes_sop_dlpfc0 <- brm(formula = DLPFC ~ Age + Patient, data = d2_cognition, family = gaussian, save_all_pars = TRUE, iter = 2000*20) #(iter is high because bridgesampling for Bayes Factor requires it)

#Plot diagnostics of sampling
plot(bayes_sop_dlpfc1)
plot(bayes_sop_dlpfc0)

#Summarize models
summary(bayes_sop_dlpfc1)
summary(bayes_sop_dlpfc0)

#Calculate Bayes Factor
#Estimated Bayes factor in favor of bayes_vl_dlpfc1 over bayes_vl_dlpfc0:
BF10_sop_dlpfc <- bayes_factor(bayes_sop_dlpfc1, bayes_sop_dlpfc0) 
#To get BF0/1, divide 1 by the above BF
BF01_sop_dlpfc <- 1/BF10_sop_dlpfc$bf

```

##  Exploratory analyses of D2R levels at baseline and cognitive function at follow-up



```{r, echo=FALSE}

#EXPLORATORY ANALYSES - D2R AT BASELINE RELATED TO COGNITION AT FOLLOW UP
#Load cognition file with all patients and controls at follow up
cognition_fu <- read_excel("/Users/marialee/ownCloud/FLB457_psychosis/DerivedData/Cognition/MCCB_all_191202_FU_raw.xlsx")

#Change "CPT" variable to numeric
cognition_fu$CPT <- as.numeric(cognition_fu$CPT, na.rm = TRUE)

#Flip TMT test scores so that higher values are better.
cognition_fu$TMT_f <- ((max(cognition_fu$TMT) - cognition_fu$TMT) + min(cognition_fu$TMT))

#Make domain score Speed of Processing from TMT, BACS and Fluency, using raw scores
cognition_fu <- cognition_fu %>% mutate(SOP = (TMT_f + BACS + Fluency)/3)
#Make domain score Working Memory from WMS_III and LNS, using raw scores
cognition_fu <- cognition_fu %>% mutate(WM = (WMS_III + LNS)/2)
#Make neurocognitive domain score using SOP, WM, HVLT-R, Mazes, BVMT-R, CPT, using raw scores
cognition_fu <- cognition_fu %>% mutate(Neurocog = (SOP + WM + HVLT_R + Mazes + BVMT_R + CPT/6))

#Wrangling data to be able to handle NA:s when adding age-corrected residuals; the Vincent approach (row names)
cognition_fu <- as.data.frame(cognition_fu) #Making it a data.frame because it doesn't work with tibble
new_name_fu <- cognition_fu$KASP_id
cognition_fu <- data.frame(cognition_fu, row.names = new_name_fu)

wcst_fu <- as.data.frame(wcst_fu)
new_name_wcst_fu <- wcst_fu$ClientID
wcst_fu <- data.frame(wcst_fu, row.names = new_name_wcst_fu)

#Make a regression model and extract the residuals, using the whole client sample for better correction
#Verbal Learning
model_verblearnFU <- lm(formula = HVLT_R ~ Age_FU, cognition_fu) #Regression model
agecorr_verblearn_resid <- model_verblearnFU$residuals #Extracting residuals
agecorr_verblearn_resid <- data.frame(names(agecorr_verblearn_resid), agecorr_verblearn_resid)
#Making residuals into data.frame to be able to join together with cognition data.frame in next step
#Working Memory
model_wmFU <- lm(formula = WM ~ Age_FU, cognition_fu) 
agecorr_wm_resid <- model_wmFU$residuals
agecorr_wm_resid <- data.frame(names(agecorr_wm_resid), agecorr_wm_resid)
#Speed of Processing
model_sopFU <- lm(formula = SOP ~ Age_FU, cognition_fu) 
agecorr_sop_resid <- model_sopFU$residuals
agecorr_sop_resid <- data.frame(names(agecorr_sop_resid), agecorr_sop_resid)
#Visual Learning
model_vis_learnFU <- lm(formula = BVMT_R ~ Age_FU, cognition_fu) 
agecorr_vis_learn_resid <- model_vis_learnFU$residuals
agecorr_vis_learn_resid <- data.frame(names(agecorr_vis_learn_resid), agecorr_vis_learn_resid)
#Attention
model_cptFU <- lm(formula = CPT ~ Age_FU, cognition_fu) 
agecorr_cpt_resid <- model_cptFU$residuals
agecorr_cpt_resid <- data.frame(names(agecorr_cpt_resid), agecorr_cpt_resid)
#General Cognitive Ability
model_neuro_cogFU <- lm(formula = Neurocog ~ Age_FU, cognition_fu) 
agecorr_neuro_cog_resid <- model_neuro_cogFU$residuals
agecorr_neuro_cog_resid <- data.frame(names(agecorr_neuro_cog_resid), agecorr_neuro_cog_resid)
#Executive Function
model_wcstFU <- lm(formula = PctErrors ~ AgeYr, wcst_fu)
agecorr_wcst_resid <- model_wcstFU$residuals
agecorr_wcst_resid <- data.frame(names(agecorr_wcst_resid), agecorr_wcst_resid)

#Add residuals to cognition data.frame, using full_join
cognition_fu <- full_join(cognition_fu, agecorr_verblearn_resid, by = c("KASP_id" = "names.agecorr_verblearn_resid."))
cognition_fu <- full_join(cognition_fu, agecorr_wm_resid, by = c("KASP_id" = "names.agecorr_wm_resid."))
cognition_fu <- full_join(cognition_fu, agecorr_sop_resid, by = c("KASP_id" = "names.agecorr_sop_resid."))
cognition_fu <- full_join(cognition_fu, agecorr_vis_learn_resid, by = c("KASP_id" = "names.agecorr_vis_learn_resid."))
cognition_fu <- full_join(cognition_fu, agecorr_cpt_resid, by = c("KASP_id" = "names.agecorr_cpt_resid."))
cognition_fu <- full_join(cognition_fu, agecorr_neuro_cog_resid, by = c("KASP_id" = "names.agecorr_neuro_cog_resid."))

#Executive Function 
wcst_fu <- full_join(wcst_fu, agecorr_wcst_resid, by = c("ClientID" = "names.agecorr_wcst_resid."))

#Standardizing the age-corrected residuals for more interpretable beta-estimates
cognition_fu <- cognition_fu %>% 
                  mutate_at(.vars = vars("agecorr_verblearn_resid", "agecorr_wm_resid", "agecorr_sop_resid", "agecorr_vis_learn_resid", 
"agecorr_cpt_resid", "agecorr_neuro_cog_resid"),
                            .funs = list(~scale(.) %>% as.vector))
wcst_fu <- wcst_fu %>% mutate_at(.vars = vars("agecorr_wcst_resid"),
                           .funs = list(~scale(.)%>% as.vector))

#Merge PET dataset with Cognition dataset, for the PET subjects only
d2_cog_fu <- dplyr::inner_join(bpnd, cognition_fu) #Cognition (MCCB) and PET subjects
d2_wcst_fu <- dplyr::inner_join(bpnd, wcst_fu) #Cognition (WCST) and PET subjects

#Filter out controls
d2_cog_fu <- dplyr::filter(d2_cog_fu, Patient == 1)
d2_wcst_fu <- dplyr::filter(d2_wcst_fu, Patient == 1)

#No centering of age variable or bpnd variable was made for these analyses, as they only contain patients, making interaction effect irrelevant  

```


###  Regression models of BPND at baseline and cognitive results at follow-up


```{r, echo=FALSE}

#Regression models
#EXPLORATORY ANALYSIS PART 3, BPND AT BASELINE AND COGNITION AT FOLLOW-UP
#ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
model_vl_dlpfcFU <- lm(formula = DLPFC ~ agecorr_verblearn_resid + Age_FU, data = d2_cog_fu)
summary(model_vl_dlpfcFU)
round(confint(model_vl_dlpfcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$DLPFC,d2_cog_fu$agecorr_verblearn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
model_vl_hipFU <- lm(formula = HIP ~ agecorr_verblearn_resid + Age_FU, data = d2_cog_fu)
summary(model_vl_hipFU)
round(confint(model_vl_hipFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$HIP,d2_cog_fu$agecorr_verblearn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 3 - VERBAL LEARNING AND D2R IN THALAMUS
model_vl_thaFU <- lm(formula = THA ~ agecorr_verblearn_resid + Age_FU, data = d2_cog_fu)
summary(model_vl_thaFU)
round(confint(model_vl_thaFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$THA,d2_cog_fu$agecorr_verblearn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 4 - VERBAL LEARNING AND D2R IN ACC
model_vl_accFU <- lm(formula = ACC ~ agecorr_verblearn_resid + Age_FU, data = d2_cog_fu)
summary(model_vl_accFU)
round(confint(model_vl_accFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$ACC,d2_cog_fu$agecorr_verblearn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 5 - VERBAL LEARNING AND D2R IN TC
model_vl_tcFU <- lm(formula = TC ~ agecorr_verblearn_resid + Age_FU, data = d2_cog_fu)
summary(model_vl_tcFU)
round(confint(model_vl_tcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$TC,d2_cog_fu$agecorr_verblearn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 6 - WORKING MEMORY AND D2R IN DLPFC
model_wm_dlpfcFU <- lm(formula = DLPFC ~ agecorr_wm_resid + Age_FU, data = d2_cog_fu)
summary(model_wm_dlpfcFU)
round(confint(model_wm_dlpfcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$DLPFC,d2_cog_fu$agecorr_wm_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 7 - WORKING MEMORY AND D2R IN THA
model_wm_thaFU <- lm(formula = THA ~ agecorr_wm_resid + Age_FU, data = d2_cog_fu)
summary(model_wm_thaFU)
round(confint(model_wm_thaFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$THA,d2_cog_fu$agecorr_wm_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 8 - WORKING MEMORY AND D2R IN ACC
model_wm_accFU <- lm(formula = ACC ~ agecorr_wm_resid + Age_FU, data = d2_cog_fu)
summary(model_wm_accFU)
round(confint(model_wm_accFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$ACC,d2_cog_fu$agecorr_wm_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 9 - WORKING MEMORY AND D2R IN HIP
model_wm_hipFU <- lm(formula = HIP ~ agecorr_wm_resid + Age_FU, data = d2_cog_fu)
summary(model_wm_hipFU)
round(confint(model_wm_hipFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$HIP,d2_cog_fu$agecorr_wm_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 10 - WORKING MEMORY AND D2R IN TC
model_wm_tcFU <- lm(formula = TC ~ agecorr_wm_resid + Age_FU, data = d2_cog_fu)
summary(model_wm_tcFU)
round(confint(model_wm_tcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$TC,d2_cog_fu$agecorr_wm_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 11 - SPEED OF PROCESSING AND D2R IN DLPFC
model_sop_dlpfcFU <- lm(formula = DLPFC ~ agecorr_sop_resid + Age_FU, data = d2_cog_fu)
summary(model_sop_dlpfcFU)
round(confint(model_sop_dlpfcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$DLPFC,d2_cog_fu$agecorr_sop_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 12 - SPEED OF PROCESSING AND D2R IN HIP
model_sop_hipFU <- lm(formula = HIP ~ agecorr_sop_resid + Age_FU, data = d2_cog_fu)
summary(model_sop_hipFU)
round(confint(model_sop_hipFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$HIP,d2_cog_fu$agecorr_sop_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 13 - SPEED OF PROCESSING AND D2R IN THA
model_sop_thaFU <- lm(formula = THA ~ agecorr_sop_resid + Age_FU, data = d2_cog_fu)
summary(model_sop_thaFU)
round(confint(model_sop_thaFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$THA,d2_cog_fu$agecorr_sop_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 14 - SPEED OF PROCESSING AND D2R IN ACC
model_sop_accFU <- lm(formula = ACC ~ agecorr_sop_resid + Age_FU, data = d2_cog_fu)
summary(model_sop_accFU)
round(confint(model_sop_accFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$ACC,d2_cog_fu$agecorr_sop_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 15 - SPEED OF PROCESSING AND D2R IN TC
model_sop_tcFU <- lm(formula = TC ~ agecorr_sop_resid + Age_FU, data = d2_cog_fu)
summary(model_sop_tcFU)
round(confint(model_sop_tcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$TC,d2_cog_fu$agecorr_sop_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 16 - ATTENTION AND D2R IN DLPFC
model_cpt_dlpfcFU <- lm(formula = DLPFC ~ agecorr_cpt_resid + Age_FU, data = d2_cog_fu)
summary(model_cpt_dlpfcFU)
round(confint(model_cpt_dlpfcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$DLPFC,d2_cog_fu$agecorr_cpt_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 17 - ATTENTION AND D2R IN THA
model_cpt_thaFU <- lm(formula = THA ~ agecorr_cpt_resid + Age_FU, data = d2_cog_fu)
summary(model_cpt_thaFU)
round(confint(model_cpt_thaFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$THA,d2_cog_fu$agecorr_cpt_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 18 - ATTENTION AND D2R IN ACC
model_cpt_accFU <- lm(formula = ACC ~ agecorr_cpt_resid + Age_FU, data = d2_cog_fu)
summary(model_cpt_accFU)
round(confint(model_cpt_accFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$ACC,d2_cog_fu$agecorr_cpt_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 19 - ATTENTION AND D2R IN HIP
model_cpt_hipFU <- lm(formula = HIP ~ agecorr_cpt_resid + Age_FU, data = d2_cog_fu)
summary(model_cpt_hipFU)
round(confint(model_cpt_hipFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$HIP,d2_cog_fu$agecorr_cpt_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 20 - ATTENTION AND D2R IN TC
model_cpt_tcFU <- lm(formula = TC ~ agecorr_cpt_resid + Age_FU, data = d2_cog_fu)
summary(model_cpt_tcFU)
round(confint(model_cpt_tcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$TC,d2_cog_fu$agecorr_cpt_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 21 - VISUAL LEARNING AND D2R IN DLPFC
model_vis_learn_dlpfcFU <- lm(formula = DLPFC ~ agecorr_vis_learn_resid + Age_FU, data = d2_cog_fu)
summary(model_vis_learn_dlpfcFU)
round(confint(model_vis_learn_dlpfcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$DLPFC,d2_cog_fu$agecorr_vis_learn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 22 - VISUAL LEARNING AND D2R IN THA
model_vis_learn_thaFU <- lm(formula = THA ~ agecorr_vis_learn_resid + Age_FU, data = d2_cog_fu)
summary(model_vis_learn_thaFU)
round(confint(model_vis_learn_thaFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$THA,d2_cog_fu$agecorr_vis_learn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 23 - VISUAL LEARNING AND D2R IN ACC
model_vis_learn_accFU <- lm(formula = ACC ~ agecorr_vis_learn_resid + Age_FU, data = d2_cog_fu)
summary(model_vis_learn_accFU)
round(confint(model_vis_learn_accFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$ACC,d2_cog_fu$agecorr_vis_learn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 24 - VISUAL LEARNING AND D2R IN HIP
model_vis_learn_hipFU <- lm(formula = HIP ~ agecorr_vis_learn_resid + Age_FU, data = d2_cog_fu)
summary(model_vis_learn_hipFU)
round(confint(model_vis_learn_hipFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$HIP,d2_cog_fu$agecorr_vis_learn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 25 - VISUAL LEARNING AND D2R IN TC
model_vis_learn_tcFU <- lm(formula = TC ~ agecorr_vis_learn_resid + Age_FU, data = d2_cog_fu)
summary(model_vis_learn_tcFU)
round(confint(model_vis_learn_tcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$TC,d2_cog_fu$agecorr_vis_learn_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 26 - GENERAL COGNITIVE ABILITY AND D2R IN DLPFC
model_neuro_cog_dlpfcFU <- lm(formula = DLPFC ~ agecorr_neuro_cog_resid + Age_FU, data = d2_cog_fu)
summary(model_neuro_cog_dlpfcFU)
round(confint(model_neuro_cog_dlpfcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$DLPFC,d2_cog_fu$agecorr_neuro_cog_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 27 - GENERAL COGNITIVE ABILITY AND D2R IN HIP
model_neuro_cog_hipFU <- lm(formula = HIP ~ agecorr_neuro_cog_resid + Age_FU, data = d2_cog_fu)
summary(model_neuro_cog_hipFU)
round(confint(model_neuro_cog_hipFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$HIP,d2_cog_fu$agecorr_neuro_cog_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 28 - GENERAL COGNITIVE ABILITY AND D2R IN THA
model_neuro_cog_thaFU <- lm(formula = THA ~ agecorr_neuro_cog_resid + Age_FU, data = d2_cog_fu)
summary(model_neuro_cog_thaFU)
round(confint(model_neuro_cog_thaFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$THA,d2_cog_fu$agecorr_neuro_cog_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 29 - GENERAL COGNITIVE ABILITY AND D2R IN ACC
model_neuro_cog_accFU <- lm(formula = ACC ~ agecorr_neuro_cog_resid + Age_FU, data = d2_cog_fu)
summary(model_neuro_cog_accFU)
round(confint(model_neuro_cog_accFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$ACC,d2_cog_fu$agecorr_neuro_cog_resid, d2_cog_fu[,c("Age_FU")])

#ANALYSIS 30 - GENERAL COGNITIVE ABILITY AND D2R IN TC
model_neuro_cog_tcFU <- lm(formula = TC ~ agecorr_neuro_cog_resid + Age_FU, data = d2_cog_fu)
summary(model_neuro_cog_tcFU)
round(confint(model_neuro_cog_tcFU), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_fu$TC,d2_cog_fu$agecorr_neuro_cog_resid, d2_cog_fu[,c("Age_FU")])

#ONLY 8 INDIVIDUALS...

#EXPLORATORY ANALYSIS 21 - EXECUTIVE FUNCTION AND D2R IN DLPFC
#model_wcst_dlpfc <- lm(formula = DLPFC ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
#summary(model_wcst_dlpfc)
#round(confint(model_wcst_dlpfc), digits = 3)
#Partial correlation for the same relationship
#pcor.test(d2_wcst$DLPFC,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 22 - EXECUTIVE FUNCTION AND D2R IN HIP
#model_wcst_hip <- lm(formula = HIP ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
#summary(model_wcst_hip)
#round(confint(model_wcst_hip), digits = 3)
#Partial correlation for the same relationship
#pcor.test(d2_wcst$HIP,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 23 - EXECUTIVE FUNCTION AND D2R IN THA
#model_wcst_tha <- lm(formula = THA ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
#summary(model_wcst_tha)
#round(confint(model_wcst_tha), digits = 3)
#Partial correlation for the same relationship
#pcor.test(d2_wcst$THA,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 24 - EXECUTIVE FUNCTION AND D2R IN ACC
#model_wcst_acc <- lm(formula = ACC ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
#summary(model_wcst_acc)
#round(confint(model_wcst_acc), digits = 3)
#Partial correlation for the same relationship
#pcor.test(d2_wcst$ACC,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])

#EXPLORATORY ANALYSIS 25 - EXECUTIVE FUNCTION AND D2R IN TC
#model_wcst_tc <- lm(formula = TC ~ agecorr_wcst_residuals + AgeYr + Patient, data = d2_wcst)
#summary(model_wcst_tc)
#round(confint(model_wcst_tc), digits = 3)
#Partial correlation for the same relationship
#pcor.test(d2_wcst$TC,d2_wcst$agecorr_wcst_residuals, d2_wcst[,c("AgeYr","Patient")])


```



###  Regression models of BPND at baseline and change in cognitive results at follow-up



```{r, echo=FALSE}
#Constructing the cognitive change variables. 
d2_cog <- dplyr::select(d2_cognition, subject, Age, agecorr_verblearn_residuals:agecorr_neuro_cog_residuals) #Keep cognitive variables from baseline
d2_cog_c <- dplyr::inner_join(d2_cog, d2_cog_fu) #Add to new data.frame
#Make variables for the change in cognitive results from baseline to FU
d2_cog_c <- d2_cog_c %>% mutate(verb_learn_change = agecorr_verblearn_resid - agecorr_verblearn_residuals, wm_change = agecorr_wm_resid - agecorr_wm_residuals, sop_change = agecorr_sop_resid - agecorr_sop_residuals, cpt_change = agecorr_cpt_resid - agecorr_cpt_residuals, vis_learn_change = agecorr_vis_learn_resid - agecorr_vis_learn_residuals, neuro_cog_change = agecorr_neuro_cog_resid - agecorr_neuro_cog_residuals)

#Regression models
#EXPLORATORY ANALYSIS PART 4, BPND AT BASELINE AND CHANGE IN COGNITION FROM BASELINE TO FOLLOW-UP
#ANALYSIS 1 - VERBAL LEARNING AND D2R IN DLPFC
model_vl_dlpfcC <- lm(formula = DLPFC ~ verb_learn_change + Age, data = d2_cog_c)
summary(model_vl_dlpfcC)
round(confint(model_vl_dlpfcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$DLPFC,d2_cog_c$verb_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 2 - VERBAL LEARNING AND D2R IN HIPPOCAMPUS
model_vl_hipC <- lm(formula = HIP ~ verb_learn_change + Age, data = d2_cog_c)
summary(model_vl_hipC)
round(confint(model_vl_hipC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$HIP,d2_cog_c$verb_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 3 - VERBAL LEARNING AND D2R IN THALAMUS
model_vl_thaC <- lm(formula = THA ~ verb_learn_change + Age, data = d2_cog_c)
summary(model_vl_thaC)
round(confint(model_vl_thaC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$THA,d2_cog_c$verb_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 4 - VERBAL LEARNING AND D2R IN ACC
model_vl_ACCC <- lm(formula = ACC ~ verb_learn_change + Age, data = d2_cog_c)
summary(model_vl_ACCC)
round(confint(model_vl_ACCC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$ACC,d2_cog_c$verb_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 5 - VERBAL LEARNING AND D2R IN TC
model_vl_tcC <- lm(formula = TC ~ verb_learn_change + Age, data = d2_cog_c)
summary(model_vl_tcC)
round(confint(model_vl_tcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$TC,d2_cog_c$verb_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 6 - WORKING MEMORY AND D2R IN DLPFC
model_wm_dlpfcC <- lm(formula = DLPFC ~ wm_change + Age, data = d2_cog_c)
summary(model_wm_dlpfcC)
round(confint(model_wm_dlpfcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$DLPFC,d2_cog_c$wm_change, d2_cog_c[,c("Age")])

#ANALYSIS 7 - WORKING MEMORY AND D2R IN THA
model_wm_thaC <- lm(formula = THA ~ wm_change + Age, data = d2_cog_c)
summary(model_wm_thaC)
round(confint(model_wm_thaC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$THA,d2_cog_c$wm_change, d2_cog_c[,c("Age")])

#ANALYSIS 8 - WORKING MEMORY AND D2R IN ACC
model_wm_accC <- lm(formula = ACC ~ wm_change + Age, data = d2_cog_c)
summary(model_wm_accC)
round(confint(model_wm_accC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$ACC,d2_cog_c$wm_change, d2_cog_c[,c("Age")])

#ANALYSIS 9 - WORKING MEMORY AND D2R IN HIP
model_wm_hipC <- lm(formula = HIP ~ wm_change + Age, data = d2_cog_c)
summary(model_wm_hipC)
round(confint(model_wm_hipC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$HIP,d2_cog_c$wm_change, d2_cog_c[,c("Age")])

#ANALYSIS 10 - WORKING MEMORY AND D2R IN TC
model_wm_tcC <- lm(formula = TC ~ wm_change + Age, data = d2_cog_c)
summary(model_wm_tcC)
round(confint(model_wm_tcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$TC,d2_cog_c$wm_change, d2_cog_c[,c("Age")])

#ANALYSIS 11 - SPEED OF PROCESSING AND D2R IN DLPFC
model_sop_dlpfcC <- lm(formula = DLPFC ~ sop_change + Age, data = d2_cog_c)
summary(model_sop_dlpfcC)
round(confint(model_sop_dlpfcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$DLPFC,d2_cog_c$sop_change, d2_cog_c[,c("Age")])

#ANALYSIS 12 - SPEED OF PROCESSING AND D2R IN HIP
model_sop_hipC <- lm(formula = HIP ~ sop_change + Age, data = d2_cog_c)
summary(model_sop_hipC)
round(confint(model_sop_hipC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$HIP,d2_cog_c$sop_change, d2_cog_c[,c("Age")])

#ANALYSIS 13 - SPEED OF PROCESSING AND D2R IN THA
model_sop_thaC <- lm(formula = THA ~ sop_change + Age, data = d2_cog_c)
summary(model_sop_thaC)
round(confint(model_sop_thaC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$THA,d2_cog_c$sop_change, d2_cog_c[,c("Age")])

#ANALYSIS 14 - SPEED OF PROCESSING AND D2R IN ACC
model_sop_accC <- lm(formula = ACC ~ sop_change + Age, data = d2_cog_c)
summary(model_sop_accC)
round(confint(model_sop_accC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$ACC,d2_cog_c$sop_change, d2_cog_c[,c("Age")])

#ANALYSIS 15 - SPEED OF PROCESSING AND D2R IN TC
model_sop_tcC <- lm(formula = TC ~ sop_change + Age, data = d2_cog_c)
summary(model_sop_tcC)
round(confint(model_sop_tcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$TC,d2_cog_c$sop_change, d2_cog_c[,c("Age")])

#ANALYSIS 16 - ATTENTION AND D2R IN DLPFC
model_cpt_dlpfcC <- lm(formula = DLPFC ~ cpt_change + Age, data = d2_cog_c)
summary(model_cpt_dlpfcC)
round(confint(model_cpt_dlpfcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$DLPFC,d2_cog_c$cpt_change, d2_cog_c[,c("Age")])

#ANALYSIS 17 - ATTENTION AND D2R IN THA
model_cpt_thaC <- lm(formula = THA ~ cpt_change + Age, data = d2_cog_c)
summary(model_cpt_thaC)
round(confint(model_cpt_thaC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$THA,d2_cog_c$cpt_change, d2_cog_c[,c("Age")])

#ANALYSIS 18 - ATTENTION AND D2R IN ACC
model_cpt_accC <- lm(formula = ACC ~ cpt_change + Age, data = d2_cog_c)
summary(model_cpt_accC)
round(confint(model_cpt_accC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$ACC,d2_cog_c$cpt_change, d2_cog_c[,c("Age")])

#ANALYSIS 19 - ATTENTION AND D2R IN HIP
model_cpt_hipC <- lm(formula = HIP ~ cpt_change + Age, data = d2_cog_c)
summary(model_cpt_hipC)
round(confint(model_cpt_hipC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$HIP,d2_cog_c$cpt_change, d2_cog_c[,c("Age")])

#ANALYSIS 20 - ATTENTION AND D2R IN TC
model_cpt_tcC <- lm(formula = TC ~ cpt_change + Age, data = d2_cog_c)
summary(model_cpt_tcC)
round(confint(model_cpt_tcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$TC,d2_cog_c$cpt_change, d2_cog_c[,c("Age")])

#ANALYSIS 21 - VISUAL LEARNING AND D2R IN DLPFC
model_vis_learn_dlpfcC <- lm(formula = DLPFC ~ vis_learn_change + Age, data = d2_cog_c)
summary(model_vis_learn_dlpfcC)
round(confint(model_vis_learn_dlpfcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$DLPFC,d2_cog_c$vis_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 22 - VISUAL LEARNING AND D2R IN THA
model_vis_learn_thaC <- lm(formula = THA ~ vis_learn_change + Age, data = d2_cog_c)
summary(model_vis_learn_thaC)
round(confint(model_vis_learn_thaC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$THA,d2_cog_c$vis_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 23 - VISUAL LEARNING AND D2R IN ACC
model_vis_learn_accC <- lm(formula = ACC ~ vis_learn_change + Age, data = d2_cog_c)
summary(model_vis_learn_accC)
round(confint(model_vis_learn_accC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$ACC,d2_cog_c$vis_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 24 - VISUAL LEARNING AND D2R IN HIP
model_vis_learn_hipC <- lm(formula = HIP ~ vis_learn_change + Age, data = d2_cog_c)
summary(model_vis_learn_hipC)
round(confint(model_vis_learn_hipC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$HIP,d2_cog_c$vis_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 25 - VISUAL LEARNING AND D2R IN TC
model_vis_learn_tcC <- lm(formula = TC ~ vis_learn_change + Age, data = d2_cog_c)
summary(model_vis_learn_tcC)
round(confint(model_vis_learn_tcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$TC,d2_cog_c$vis_learn_change, d2_cog_c[,c("Age")])

#ANALYSIS 26 - GENERAL COGNITIVE ABILITY AND D2R IN DLPFC
model_neuro_cog_dlpfcC <- lm(formula = DLPFC ~ neuro_cog_change + Age, data = d2_cog_c)
summary(model_neuro_cog_dlpfcC)
round(confint(model_neuro_cog_dlpfcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$DLPFC,d2_cog_c$neuro_cog_change, d2_cog_c[,c("Age")])

#ANALYSIS 27 - GENERAL COGNITIVE ABILITY AND D2R IN HIP
model_neuro_cog_hipC <- lm(formula = HIP ~ neuro_cog_change + Age, data = d2_cog_c)
summary(model_neuro_cog_hipC)
round(confint(model_neuro_cog_hipC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$HIP,d2_cog_c$neuro_cog_change, d2_cog_c[,c("Age")])

#ANALYSIS 28 - GENERAL COGNITIVE ABILITY AND D2R IN THA
model_neuro_cog_thaC <- lm(formula = THA ~ neuro_cog_change + Age, data = d2_cog_c)
summary(model_neuro_cog_thaC)
round(confint(model_neuro_cog_thaC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$THA,d2_cog_c$neuro_cog_change, d2_cog_c[,c("Age")])

#ANALYSIS 29 - GENERAL COGNITIVE ABILITY AND D2R IN ACC
model_neuro_cog_accC <- lm(formula = ACC ~ neuro_cog_change + Age, data = d2_cog_c)
summary(model_neuro_cog_accC)
round(confint(model_neuro_cog_accC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$ACC,d2_cog_c$neuro_cog_change, d2_cog_c[,c("Age")])

#ANALYSIS 30 - GENERAL COGNITIVE ABILITY AND D2R IN TC
model_neuro_cog_tcC <- lm(formula = TC ~ neuro_cog_change + Age, data = d2_cog_c)
summary(model_neuro_cog_tcC)
round(confint(model_neuro_cog_tcC), digits = 3)
#Partial correlation for the same relationship
pcor.test(d2_cog_c$TC,d2_cog_c$neuro_cog_change, d2_cog_c[,c("Age")])

```

